Probabilistic Catalogs for Crowded Stellar Fields

### 2013-02-27 paper/ms.tex
More mods of abstract

\begin{abstract}
We present a probabilistic (Bayesian) method for producing catalogs
from images of stellar fields. The method is capable of inferring the
number of sources $N$ in the image and can also handle the
challenges introduced by overlapping sources. The luminosity
function of the stars can also be inferred even when the precise luminosity
of each star is uncertain. The computational feasibility of the method is
demonstrated on simulated data where the luminosity function of the stars is a
broken power-law. We compare the results obtained from our method
with those obtained from the \sex~software and find that the latter ...
\end{abstract}

>>>>

\begin{abstract}
We present a probabilistic (Bayesian) method for producing catalogs
from images of stellar fields. The method is capable of inferring the
number of sources $N$ in the image and can also handle the
challenges introduced by noise and overlapping sources. The luminosity
function of the stars can also be inferred even when the precise luminosity
of each star is uncertain, via the use of a hierarchical Bayesian model.
The computational feasibility of the method is
demonstrated on simulated data where the luminosity function of the stars is a
broken power-law. We compare the results obtained from our method
with those obtained from the popular \sex~software and find that our method
... . We conclude that the inferences from our method are more reliable,
especially in the case where the field is crowded with many overlapping stars.
\end{abstract}
